Who Needs Privacy?

### 2018-12-09 results/archive/analyses_2018-11-21_before filtering.RmD
- major updates on everything:     - mostly finished the analyses     - rewritten the methods, results, and abstract

```{r r-setup, include=F, echo=F}
# list packages to be used
packages <- c("devtools", "lavaan", "MBESS", "magrittr", "psych", "semPlot", "tidyverse")

@@

# recode
d <- d %>% 
  mutate_at(vars(RIT_1:RIT_8), funs(as.numeric(.)))
```

@@

```{r, fig.height=15, fig.width=12}
d_tmp <- select(d, starts_with("N4P"))
name_tmp <- "pri_nee"
recoded_tmp <- c("N4P.INT_1", "N4P.INT_5", "N4P.INT_8")

@@

# recode
d[recoded_tmp] <- 8 - d[recoded_tmp]
d_tmp <- select(d, starts_with("N4P"))  # new selection bc of recoding
```

@@

```{r}
tmp <- omega(select(d_tmp, 
                    -N4P.BOT_4, -N4P.BOT_3, -N4P.SOC_7, -N4P.INT_5, -N4P.INT_3), 
             nfactors = 4, fm = "ml")
```

@@

```{r}
tmp <- omega(select(d_tmp,
                    -N4P.BOT_4, -N4P.BOT_3, -N4P.INT_5, -N4P.INT_3, -N4P.INT_7, -N4P.INT_4), 
             nfactors = 3, fm = "ml")
```

@@

```{r, fig.height=8, fig.width=12}
d_tmp <- select(d, starts_with("INT_"))
name_tmp <- "int"
recoded_tmp <- c("INT_1", "INT_2", "INT_5", "INT_6", "INT_7", 
                 "INT_8", "INT_9", "INT_10", "INT_11")

@@

# recode
d[recoded_tmp] <- 8 - d[recoded_tmp]
d_tmp <- select(d, starts_with("INT_"))  # new selection bc of recoding
```

@@

```{r}
tmp <- omega(select(d_tmp, -INT_3, -INT_4), fm = "ml", nfactors = 2)
```

@@

```{r}
model <- '
  int_1 =~ INT_1 + INT_2 + a*INT_5 + a*INT_6 + a*INT_7 + INT_8
  int_2 =~ b*INT_8 + b*INT_9 + b*INT_10 + b*INT_11
  int_gen =~ INT_1 + INT_2 + INT_5 + INT_6 + INT_7 + INT_8 + INT_9 + INT_10 + INT_11
  int_gen ~~ 0*int_1 + 0*int_2
  int_1 ~~ 0*int_2
'
fit <- cfa(model, d, missing = "ml")
summary(fit, fit = TRUE, std = TRUE)
assign(paste0(name_tmp, "_fit"), 
       cfa(model, d))
assign(paste0(name_tmp, "_gen"), 
       select(as.data.frame(predict(fit)), ends_with("_gen")))
```

@@

```{r, fig.height=8, fig.width=12}
d_tmp <- select(d, SOC_1 : SOC_8)
name_tmp <- "soc"
recoded_tmp <- c("SOC_1", "SOC_3", "SOC_5", "SOC_7")

@@

# recode
d[recoded_tmp] <- 8 - d[recoded_tmp]
d_tmp <- select(d, SOC_1 : SOC_8)  # new selection bc of recoding
```

@@

```{r}
model <- '
  soc_1 =~ a*SOC_1 + SOC_3 + SOC_5 + a*SOC_7
  soc_2 =~ b*SOC_2 + SOC_4 + SOC_6 + b*SOC_8 + SOC_1 + SOC_7
  soc_gen =~ SOC_1 + SOC_2 + SOC_3 + SOC_4 + SOC_5 + SOC_6 + SOC_7 + SOC_8
  soc_gen ~~ 0*soc_1 + 0*soc_2
  soc_1 ~~ 0*soc_2
'
fit <- cfa(model, d, missing = "ml")
summary(fit, fit = TRUE, std = TRUE)
assign(paste0(name_tmp, "_fit"), 
       cfa(model, d))
assign(paste0(name_tmp, "_gen"), 
       select(as.data.frame(predict(fit)), ends_with("_gen")))
```

@@

```{r}
d_tmp <- select(d, starts_with("FEA_"))
name_tmp <- "fea"
recoded_tmp <- c("FEA_1", "FEA_3", "FEA_5", "FEA_7")

@@

# recode
d[recoded_tmp] <- 8 - d[recoded_tmp]
d_tmp <- select(d, starts_with("FEA_"))  # new selection bc of recoding
```

@@

  fea_gen ~~ 0*fea_1 + 0*fea_2
  fea_1 ~~ 0*fea_2
'
fit <- cfa(model, d, missing = "ml")
summary(fit, fit = TRUE, std = TRUE)
assign(paste0(name_tmp, "_fit"), cfa(model, d))
assign(paste0(name_tmp, "_gen"), 
       select(as.data.frame(predict(fit)), ends_with("_gen")))
```

@@

```{r}
d_tmp <- select(d, TRA_1 : TRA_8)
name_tmp <- "tra"
recoded_tmp <- c("TRA_2", "TRA_4", "TRA_6")

@@

# recode
d[recoded_tmp] <- 8 - d[recoded_tmp]
d_tmp <- select(d, TRA_1 : TRA_8)  # new selection bc of recoding
```

@@

  tra_gen ~~ 0*tra_1 + 0*tra_2
  tra_1 ~~ 0*tra_2
'
fit <- cfa(model, d, missing = "ml")
summary(fit, fit = TRUE, std = TRUE)
assign(paste0(name_tmp, "_fit"), cfa(model, d))
assign(paste0(name_tmp, "_gen"), 
       select(as.data.frame(predict(fit)), ends_with("_gen")))
```

@@

```{r}
d_tmp <- select(d, RIT_1 : RIT_8)
name_tmp <- "rit"
recoded_tmp <- c("RIT_1", "RIT_3", "RIT_5")

@@

# recode
d[recoded_tmp] <- 8 - d[recoded_tmp]
d_tmp <- select(d, RIT_1 : RIT_8)  # new selection bc of recoding
```

@@

  rit_gen ~~ 0*rit_1 + 0*rit_2
  rit_1 ~~ 0*rit_2
'
fit <- cfa(model, d, missing = "ml")
summary(fit, fit = TRUE, std = TRUE)
assign(paste0(name_tmp, "_fit"), cfa(model, d))
assign(paste0(name_tmp, "_gen"), 
       select(as.data.frame(predict(fit)), ends_with("_gen")))
```

@@

```{r}
d_tmp <- select(d, BFI_1 : BFI_10)
name_tmp <- "BFI"

@@

  pri_nee_gen ~ int_gen + soc_gen + fea_gen + tra_gen + rit_gen
  pri_nee_ver ~ int_gen + soc_gen + fea_gen + tra_gen + rit_gen
  pri_nee_ide ~ int_gen + soc_gen + fea_gen + tra_gen + rit_gen
  pri_nee_hor ~ int_gen + soc_gen + fea_gen + tra_gen + rit_gen

@@

  pri_nee_gen ~~ 0*pri_nee_ver + 0*pri_nee_hor + 0*pri_nee_ide
  pri_nee_ver ~~ 0*pri_nee_hor + 0*pri_nee_ide
  pri_nee_hor ~~ 0*pri_nee_ide
'
fit <- sem(model, d, missing = "ml")
summary(fit, fit = TRUE, std = TRUE)
assign(paste0(name_tmp, "_fit"), cfa(model, d))
```

## With big five

@@

```{r}
d_effects <- coeffs_tab(main_fit) %>%
  mutate(sig = ifelse(p < .05, "1", "0"))

# std_ci <- ci.src(beta.k = d_effects$beta, b.k = d_effects$b, 
#                  N = 400, conf.level = .95, SE.b.k = .10, s.Y = sqrt(.955), )

p_effects <- ggplot(d_effects, aes(x = beta)) +
  geom_point(aes(y = Predictor, color = sig)) +
  scale_color_manual(values = c("#000000", "#FF0000")) +
  geom_vline(xintercept = 0) +
  geom_vline(xintercept = 0.1, linetype = "dashed") +
  geom_vline(xintercept = -0.1, linetype = "dashed") +
  theme_bw() + 
  facet_grid(~ Outcome)
```

>>>>

```{r r-setup, include=F, echo=F}
# list packages to be used
packages <- c("devtools", "ggplot2", "influence.SEM", "lavaan", "MBESS", 
              "magrittr", "PerFit", "psych", "semPlot", "tidyverse")

@@

# edit variables
d %<>% 
  mutate(
    male = 2 - SES.SEX,
    time = V9 - V8,
    id = 1:nrow(.)
    ) %>% 
  mutate_at(vars(RIT_1:RIT_8), funs(as.numeric(.))) %>% 
  rename(
    age = SES.AGE,
    inc = SES.JOB_2
  )

# select items
d %<>% dplyr::select(
  id, male, age, inc, time,
  starts_with("N4P"),
  starts_with("INT_"),
  SOC_1 : SOC_8,
  starts_with("FEA_"),
  TRA_1 : TRA_8,
  RIT_1 : RIT_8,
  BFI_1 : BFI_10
)
items <- names(d)
```

# Data wrangling
## Delete defective data

First, we checked response times to delete inconceivably fast respondents.

```{r}
# plot reponse times
qplot(d$time)

# filter speeders (i.e., t < 180s)
d_all <- d
d <- d[d$time > 120, ]

# filter defective data
lzpoly <- lzpoly(dplyr::select(d, N4P.BOT_1:RIT_8) - 1, 7)
gpoly <- Gnormed.poly(dplyr::select(d, N4P.BOT_1:RIT_8) - 1, 7) %$% 
  PFscores %>% 
  mutate(id = d$id) %>% 
  arrange(PFscores)

# inspect cases with susceptive data
d[PFscores > .30, ]
```

@@

```{r, fig.height=15, fig.width=12}
d_tmp <- dplyr::select(d, starts_with("N4P"))
name_tmp <- "pri_nee"
recoded_tmp <- c("N4P.INT_1", "N4P.INT_5", "N4P.INT_8")

@@

# recode
d[recoded_tmp] <- 8 - d[recoded_tmp]
d_tmp <- dplyr::select(d, starts_with("N4P"))  # new selection bc of recoding
```

@@

```{r}
tmp <- omega(dplyr::select(d_tmp, 
                    -N4P.BOT_4, -N4P.BOT_3, -N4P.SOC_7, -N4P.INT_5, -N4P.INT_3), 
             nfactors = 4, fm = "ml")
```

@@

```{r}
tmp <- omega(dplyr::select(d_tmp,
                    -N4P.BOT_4, -N4P.BOT_3, -N4P.INT_5, -N4P.INT_3, -N4P.INT_7, -N4P.INT_4), 
             nfactors = 3, fm = "ml")
```

@@

```{r, fig.height=8, fig.width=12}
d_tmp <- dplyr::select(d, starts_with("INT_"))
name_tmp <- "int"
recoded_tmp <- c("INT_1", "INT_2", "INT_5", "INT_6", "INT_7", 
                 "INT_8", "INT_9", "INT_10", "INT_11")

@@

d[recoded_tmp] <- 8 - d[recoded_tmp]  # recode
d_tmp <- dplyr::select(d, starts_with("INT_"))  # new selection bc of recoding
```

@@

```{r}
tmp <- omega(dplyr::select(d_tmp, -INT_3, -INT_4), fm = "ml", nfactors = 2)
```

@@

```{r}
model <- '
  int_1 =~ INT_1 + INT_2 + a*INT_5 + a*INT_6 + a*INT_7 + INT_8
  int_2 =~ b*INT_8 + b*INT_9 + b*INT_10 + b*INT_11
  int_gen =~ INT_1 + INT_2 + INT_5 + INT_6 + INT_7 + INT_8 + INT_9 + INT_10 + INT_11
  int_gen ~~ 0*int_1 + 0*int_2
  int_1 ~~ 0*int_2
'
fit <- cfa(model, d, missing = "ml")
summary(fit, fit = TRUE, std = TRUE)
assign(paste0(name_tmp, "_fit"), 
       cfa(model, d))
assign(paste0(name_tmp, "_gen"), 
       dplyr::select(as.data.frame(predict(fit)), ends_with("_gen")))
```

@@

```{r, fig.height=8, fig.width=12}
d_tmp <- dplyr::select(d, SOC_1 : SOC_8)
name_tmp <- "soc"
recoded_tmp <- c("SOC_1", "SOC_3", "SOC_5", "SOC_7")

@@

# recode
d[recoded_tmp] <- 8 - d[recoded_tmp]
d_tmp <- dplyr::select(d, SOC_1 : SOC_8)  # new selection bc of recoding
```

@@

```{r}
model <- '
  soc_1 =~ a*SOC_1 + SOC_3 + SOC_5 + a*SOC_7
  soc_2 =~ b*SOC_2 + SOC_4 + SOC_6 + b*SOC_8 + SOC_1 + SOC_7
  soc_gen =~ SOC_1 + SOC_2 + SOC_3 + SOC_4 + SOC_5 + SOC_6 + SOC_7 + SOC_8
  soc_gen ~~ 0*soc_1 + 0*soc_2
  soc_1 ~~ 0*soc_2
'
fit <- cfa(model, d, missing = "ml")
summary(fit, fit = TRUE, std = TRUE)
assign(paste0(name_tmp, "_fit"), 
       cfa(model, d))
assign(paste0(name_tmp, "_gen"), 
       dplyr::select(as.data.frame(predict(fit)), ends_with("_gen")))
```

@@

```{r}
d_tmp <- dplyr::select(d, starts_with("FEA_"))
name_tmp <- "fea"
recoded_tmp <- c("FEA_1", "FEA_3", "FEA_5", "FEA_7")

@@

# recode
d[recoded_tmp] <- 8 - d[recoded_tmp]
d_tmp <- dplyr::select(d, starts_with("FEA_"))  # new selection bc of recoding
```

@@

  fea_gen ~~ 0*fea_1 + 0*fea_2
  fea_1 ~~ 0*fea_2
'
fit <- cfa(model, d, missing = "ml")
summary(fit, fit = TRUE, std = TRUE)
assign(paste0(name_tmp, "_fit"), cfa(model, d))
assign(paste0(name_tmp, "_gen"), 
       dplyr::select(as.data.frame(predict(fit)), ends_with("_gen")))
```

@@

```{r}
d_tmp <- dplyr::select(d, TRA_1 : TRA_8)
name_tmp <- "tra"
recoded_tmp <- c("TRA_2", "TRA_4", "TRA_6")

@@

# recode
d[recoded_tmp] <- 8 - d[recoded_tmp]
d_tmp <- dplyr::select(d, TRA_1 : TRA_8)  # new selection bc of recoding
```

@@

  tra_gen ~~ 0*tra_1 + 0*tra_2
  tra_1 ~~ 0*tra_2
'
fit <- cfa(model, d, missing = "ml")
summary(fit, fit = TRUE, std = TRUE)
assign(paste0(name_tmp, "_fit"), cfa(model, d))
assign(paste0(name_tmp, "_gen"), 
       dplyr::select(as.data.frame(predict(fit)), ends_with("_gen")))
```

@@

```{r}
d_tmp <- dplyr::select(d, RIT_1 : RIT_8)
name_tmp <- "rit"
recoded_tmp <- c("RIT_1", "RIT_3", "RIT_5")

@@

# recode
d[recoded_tmp] <- 8 - d[recoded_tmp]
d_tmp <- dplyr::select(d, RIT_1 : RIT_8)  # new selection bc of recoding
```

@@

  rit_gen ~~ 0*rit_1 + 0*rit_2
  rit_1 ~~ 0*rit_2
'
fit <- cfa(model, d, missing = "ml")
summary(fit, fit = TRUE, std = TRUE)
assign(paste0(name_tmp, "_fit"), cfa(model, d))
assign(paste0(name_tmp, "_gen"), 
       dplyr::select(as.data.frame(predict(fit)), ends_with("_gen")))
```

@@

```{r}
d_tmp <- dplyr::select(d, BFI_1 : BFI_10)
name_tmp <- "BFI"

@@

  pri_nee_gen ~ int_gen + soc_gen + fea_gen + tra_gen + rit_gen + male + age + inc
  pri_nee_ver ~ int_gen + soc_gen + fea_gen + tra_gen + rit_gen + male + age + inc
  pri_nee_ide ~ int_gen + soc_gen + fea_gen + tra_gen + rit_gen + male + age + inc
  pri_nee_hor ~ int_gen + soc_gen + fea_gen + tra_gen + rit_gen + male + age + inc

@@

  pri_nee_gen ~~ 0*pri_nee_ver + 0*pri_nee_hor + 0*pri_nee_ide
  pri_nee_ver ~~ 0*pri_nee_hor + 0*pri_nee_ide
  pri_nee_hor ~~ 0*pri_nee_ide
'
fit <- sem(model, d, estimator = "MLR")
summary(fit, fit = TRUE, std = TRUE)
fit_rem_outlier <- sem(model, filter(d, cooks_dist < 3), estimator = "MLR")
summary(fit_rem_outlier, fit = TRUE, std = TRUE)
assign(paste0(name_tmp, "_fit"), cfa(model, d))
d$cooks_dist <- cooks_dist
genCookDist(model, d, estimator = "MLR")
```

```{r}
# calculate CI for standardized effect 
# option 1: proper option, calculates extract bootstrapped coefficients for standardized solution
# CURRENTLY DOESN'T WORK
# d_effects <- bootstrapLavaan(main_fit)

# option 2: use SEs of standardized solution
d_effects <- standardizedsolution(main_fit) %>% 
  as.data.frame() %>% 
  filter(op == "~") %>% 
  mutate(lhs = factor(lhs, c("pri_nee_gen", "pri_nee_ver", "pri_nee_hor", "pri_nee_ide"))) %>%  # reorder for plot
  mutate(rhs = factor(rhs, c("inc", "age", "male", "rit_gen", "tra_gen", "fea_gen", "soc_gen", "int_gen"))) %>%  # reorder for plot
  mutate(lhs = recode(lhs, 
         `pri_nee_gen` = "Privacy need\ngeneral", 
         `pri_nee_ver` = "Privacy need\ngovernment",
         `pri_nee_hor` = "Privacy need\ninterpersonal",
         `pri_nee_ide` = "Privacy need\nanonymity")) %>% 
  mutate(rhs = recode(rhs,
         `int_gen` = "Integrity",
         `soc_gen` = "Sociability",
         `fea_gen` = "Anxiety",
         `tra_gen` = "Traditionalism",
         `rit_gen` = "Risk avoidance",
         `inc` = "Income",
         `age` = "Age",
         `male` = "Male")) %>% 
  rename(beta = est.std)

# prior solution
# d_effects <- coeffs_tab(main_fit) %>%
#   mutate(sig = ifelse(p < .05, "1", "0"))

(p_effects <- ggplot(d_effects, aes(x = beta, y = rhs)) +
  geom_point() +
  geom_errorbarh(aes(xmin = ci.lower, xmax = ci.upper, height = .2)) + 
#  scale_color_manual(values = c("#000000", "#FF0000")) +
  geom_vline(xintercept = 0) +
  geom_vline(xintercept = 0.1, linetype = "dashed", color = "grey") +
  geom_vline(xintercept = -0.1, linetype = "dashed", color = "grey") +
  theme_bw() + 
  theme(axis.title = element_blank()) +
  scale_x_continuous(breaks = seq(-.7, .7, .2)) +
  facet_grid(~ lhs))
```

# Additional Analyses
## With big five

@@
